Spfy: an integrated graph-based sequence database for real-time prediction of Escherichia coli phenotypes

### 2018-02-02 paper-webserver.tex
CHANGE: focus the first para of the discussion on this data storage as well

% drawbacks - big data
Many previous bioinformatics software programs have been developed \textit{ad hoc}, with individual researchers and laboratories developing software specific to their environment \cite{de2015trends}.
Such tools were often script-based, with custom data formats, and only suitable for small collections of data \cite{de2015trends}.
While this was acceptable for smaller analyses, bioinformatic pipelines utilizing WGS data are larger and involve linked dependencies, which would benefit from a more standardized design \cite{schatz2015biological}.
Additionally, many subsets of biology now require the analyses of big-data, where the ability to perform computations in real-time, store data in flexible databases, and utilize a common application programming interface (API) linking resources are required \cite{swaminathan2016review}.

>>>>

% drawbacks - big data
Many bioinformatics software programs have been developed \textit{ad hoc}, with individual researchers and laboratories developing software specific to their environment \cite{de2015trends}.
Such tools were often script-based, with custom data formats, and only suitable for small collections of data \cite{de2015trends}.
Recent efforts \cite{goecks2010galaxy,thomsen2016bacterial} have focused on providing a common web interface for these programs, while still returning the same result files.
However, many subsets of biology now require the analyses of big-data, where inputs are taken from a variety of analysis programs, and involve large-scale data warehousing \cite{schatz2015biological}.
The ability to perform computations in real-time, store data in flexible databases, and utilize a common application programming interface (API) linking resources are required for these analyses \cite{swaminathan2016review}.
